Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-09-02 paper/ms.tex
ditto

To place limits on the properties of a possible bound hierarchical
companion, we \added{performed the following injection-recovery
exercise.  We simulated $10^6$ two-body systems with random orbital
phases and inclinations, and semi-amplitudes and periods drawn from logarithmic
distributions: $K\ [{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^7)$,
and $P\ [{\rm days}] \sim \log \mathcal{U}(1, 10^{15})$. Again
assuming circular orbits, we then analytically evaluated what the
radial velocities would have been at the observed FEROS times if the
system had the assumed parameters.  We then calculated what the linear
slope would have been for each simulated system.  If the absolute
value of the slope exceeded our 3-$\sigma$ limit, we assumed that we
would have detected such a system.  Figure~\ref{fig:fpscenario} shows
the resulting detection limits; weakened sensitivity at harmonics of
the baseline occur at lower masses and smaller projected separations
than shown on the plot. The conversion from mass to brightness
contrast was performed using the same 35 Myr MIST isochrones and
assumptions as in
Section~\ref{subsec:speckleconstraint}.}\deleted{fitted the radial
velocity data for a Keplerian orbit assuming wide logarithmic priors
on the semi-amplitude and period: $K\ [{\rm m\,s^{-1}}] \sim
\log\mathcal{U}(1,10^5)$, and $P\ [{\rm days}] \sim \log
\mathcal{U}(0.1, 10^{15})$.  We then fitted for the semi-amplitude,
period, time of conjunction, instrument offsets, and jitter
parameters.  We converted the resulting posterior in period and
semi-amplitude to minimum mass and semi-major axis assuming Kepler's
third law.  The resulting 3-$\sigma$ limits are shown in
Figure~\ref{fig:fpscenario}.}

>>>>

To place limits on the properties of a possible bound hierarchical
companion, we \added{performed the following injection-recovery
exercise.  We simulated $10^6$ two-body systems with random orbital
phases and inclinations, and semi-amplitudes and periods drawn from logarithmic
distributions: $K\ [{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^7)$,
and $P\ [{\rm days}] \sim \log \mathcal{U}(1, 10^{15})$. Again
assuming circular orbits, we then analytically evaluated what the
radial velocities would have been at the observed FEROS times if the
system had the assumed parameters.  We then calculated what the linear
slope would have been for each simulated system.  If the absolute
value of the slope exceeded our 3-$\sigma$ limit of $|\dot{\gamma}| <
0.82\,{\rm m\,s}^{-1}\,{\rm day}^{-1}$, we assumed that we would have
detected such a system.  Figure~\ref{fig:fpscenario} shows the
resulting limits; weakened sensitivity at harmonics of the baseline
occur at lower masses and smaller projected separations than shown on
the plot. The conversion from mass to brightness contrast was
performed using the same 35 Myr MIST isochrones and assumptions as in
Section~\ref{subsec:speckleconstraint}.}\deleted{fitted the radial
velocity data for a Keplerian orbit assuming wide logarithmic priors
on the semi-amplitude and period: $K\ [{\rm m\,s^{-1}}] \sim
\log\mathcal{U}(1,10^5)$, and $P\ [{\rm days}] \sim \log
\mathcal{U}(0.1, 10^{15})$.  We then fitted for the semi-amplitude,
period, time of conjunction, instrument offsets, and jitter
parameters.  We converted the resulting posterior in period and
semi-amplitude to minimum mass and semi-major axis assuming Kepler's
third law.  The resulting 3-$\sigma$ limits are shown in
Figure~\ref{fig:fpscenario}.}
